Disease progression of 213 patients hospitalized with Covid-19 in the Czech Republic in March - October 2020: An exploratory analysis

### 2021-07-02 manuscript/manuscript.Rmd
Fixed authors for PLoS

  # rticles::plos_article:
  #   includes:
  #     in_header: preamble.tex
csl: plos.csl
#date: "Version: `r format(Sys.time(), '%Y-%m-%d')`"
author: "`r { source(here::here('manuscript', 'authors.R')); get_authors_string() }`"
---

>>>>

  # rticles::plos_article:
  #   includes:
  #     in_header: preamble.tex
csl: plos.csl
#date: "Version: `r format(Sys.time(), '%Y-%m-%d')`"
author: 
  - name: Martin Modrák
    email: martin.modrak@biomed.cas.cz
    corresponding: martin.modrak@biomed.cas.cz
    affiliation: Institute of Microbiology of the Czech Academy of Sciences
  - name: Paul-Christian Bürkner
    affiliation: University of Stuttgart
  - name: Tomáš Sieger
    affiliation: cvutCyber
  - name: Tomáš Slisz
    affiliation: 
      - resp1st
      - thomayer
  - name: Martina Vašáková
    affiliation: 
      - resp1st
      - thomayer
  - name: Grigorij Mesežnikov
    affiliation: Motol
  - name: Luis Fernando Casas-Mendez
    affiliation: Motol
  - name: Jaromír Vajter
    affiliation: Motol
  - name: Jan Táborský
    affiliation: AGEL
  - name: Viktor Kubricht
    affiliation: FNKV
  - name: Daniel Suk
    affiliation: VFN
  - name: Jan Horejsek
    affiliation: VFN
  - name: Martin Jedlička
    affiliation: Olomouc
  - name: Adriana Mifková
    affiliation: Olomouc
  - name: Adam Jaroš
    affiliation: Homolka
  - name: Miroslav Kubiska
    affiliation: Pilsen
  - name: Jana Váchalová
    affiliation: Pilsen
  - name: Robin Šín
    affiliation: Pilsen
  - name: Markéta Veverková
    affiliation: Horovice
  - name: Zbyšek Pospíšil
    affiliation: Trebic
  - name: Julie Vohryzková
    affiliation: charles2nd 
  - name: Rebeka Pokrievková
    affiliation: charles3rd
  - name: Kristián Hrušák
    affiliation: charles2nd
  - name: Kristína Christozova
    affiliation: charles2nd
  - name: Vianey Leos-Barajas
    affiliation: toronto
  - name: Karel Fišer
    affiliation: bioinfo
  - name: Tomáš Hyánek
    affiliation: Homolka
address:
  - code: Institute of Microbiology of the Czech Academy of Sciences
    address: Institute of Microbiology of the Czech Academy of Sciences, Bioinformatics Core Facility, Vídeňská 1083, Prague, Czech Republic, 142 20
  - code: University of Stuttgart
    address: University of Stuttgart, Cluster of Excellence SimTech, 	Universitätsstraße 32, Stuttgart, Deutschland, 70569
  - code: cvutCyber
    address: Dept. of Cybernetics, Faculty of Electrical Engineering, Czech Technical University in Prague, Technická 1902/2, Prague, Czech Republic, 166 27
  - code: resp1st
    address: Department of Respiratory Medicine, 1st Faculty of Medicine, Charles University in Prague, Vídeňská 800, Prague, Czech Republic, 140 59
  - code: thomayer  
    address: Thomayer University Hospital, Vídeňská 800, Prague, Czech Republic, 140 59
  - code: Motol
    address: Motol University Hospital, V Úvalu 84/1, Prague, Czech Republic, 150 06
  - code: AGEL
    address: AGEL Hospital Nový Jičín, Purkyňova 2138/16, Nový Jičín, Czech Republic, 741 01  
  - code: FNKV
    address: Kralovské Vinohrady University Hospital, Šrobárova 1150/50, Prague, Czech Republic, 100 34
  - code: VFN
    address: General University Hospital in Prague, U Nemocnice 499/2, Prague, Czech Republic, 128 08
  - code: Olomouc
    address: Military Hospital Olomouc, Sušilovo nám. 5, Olomouc, Czech Republic, 771 11
  - code: Homolka
    address: Na Homolce Hospital, Roentgenova 37, Prague, Czech Republic, 150 00
  - code: Pilsen
    address: Department of Infectious Diseases and Travel Medicine, Faculty of Medicine in Pilsen, Charles University, University Hospital in Pilsen, Edvarda Beneše 13, Pilsen, Czech Republic, 305 99
  - code: Horovice
    address: Hořovice Hospital, K Nemocnici 1106/14, Hořovice, Czech Republic, 268 01
  - code: Trebic
    address: Třebíč Hospital,  Purkyňovo nám. 133, Třebíč, Czech Republic, 674 01
  - code: charles2nd 
    address: 2nd Faculty of Medicine, Charles University in Prague, V Úvalu 84, Prague, Czech Republic, 150 06
  - code: charles3rd
    address: 3rd Faculty of Medicine, Charles University in Prague, Ruská 2411, Prague, Czech Republic, 100 00
  - code: toronto
    address: Department of Statistical Sciences, University of Toronto,  100 St George St, Toronto, Canada, ON M5S 3G3
  - code: bioinfo
    address: Department of Bioinformatics, 2nd Faculty of Medicine, Charles University in Prague, V Úvalu 84, Prague, Czech Republic, 150 06
---
